Peering Through Censorship:\\Tackling Internet Censorship Using P2P Networking

### 2023-06-01 paper.tex
werk

https://gitlab.torproject.org/tpo/anti-censorship/pluggable-transports/snowflake/-/blob/main/client/README.md
https://gitlab.torproject.org/tpo/applications/tor-browser-build/-/blob/main/projects/common/bridges_list.meek-azure.txt

[https://petsymposium.org/2015/papers/03_Fifield.pdf]
[https://signal.org/blog/looking-back-on-the-front/]
[https://arstechnica.com/information-technology/2018/04/google-disables-domain-fronting-capability-used-to-evade-censors/]

@@

[https://gfw.report/publications/usenixsecurity23/data/paper/paper.pdf]

@@

BitTorrent originated in 2001.\footnote{We use torrent and BitTorrent interchangebly throughout this paper.} It was designed to make provision of common, large files more effecient. "When a file is made available using HTTP, all upload cost is placed on the hosting machine. With BitTorrent, when multiple people are downloading the same file at the same time, they upload pieces of the file to each other. This redistributes the cost of upload to downloaders, (where it is often not even metered), this making hosting a file with a potentially unlimited number of downloaders affordable."\cite{torrent} Publishers of files choose to make their file available as a torrent, where anyone with the proper software can download it.\footnote{Nowadays, even web browsers can use extensions to access torrents.\cite{webtorrent}} At launch, users would make .torrent files available - these files contained basic info about a file - the size, name, a tracker,\footnote{"Trackers are responsible for helping downloaders find each other. They speak a very simple protocol layered on top of HTTP in which a downloader sends information about what file it’s downloading, what port it’s listening on, and similar information, and the tracker responds with a list of contact information for peers which are downloading the same file."\cite{torrent}} and hashing info.\footnote{Since then, magnet links have become an option as well. These are specifically formatted links that provide the data needed to bootstrap a torrent download without pulling a file separate from the magnet link.}\cite{torrent} The original uploader must send out at least one copy of the file being shared (or it must already be distributed out of band), but after that, the file can be reconstructed from anyone sharing the torrent rather than the original provider. Users acquire peers in a random manner from trackers, ensuring robustness. Bittorrent divides files into small pieces of fixed size, which allows users to upload before a download is completed, and these pieces are known via their SHA1 hash, ensuring file integrity. Peers announce what files they have, resulting "in less than a tenth of a percent bandwidth overhead [while] reliably utiliz[ing] all available upload capacity.\cite{torrent} BitTorrent

https://support.brave.com/hc/en-us/articles/360035025231-What-extensions-are-built-into-Brave-
https://www.bittorrent.org/bittorrentecon.pdf
https://www.usenix.org/legacy/events/imc05/tech/full_papers/guo/guo.pdf

@@

@@

IPFS is a P2P system where files are shared based on the content of the files, rather than URLs (uniform resource locaters). URLs point to specific locations, which may host whatever those in charge of the location choose to serve, assuming you can route to the specific location to acquire a file.\footnote{Routing to blocked content is indeed the primary problem that we seek to solve in the censorship circumvention sphere.} Users of IPFS (either directly or an app that performs content acquisition under the hood using IPFS) request specific files, based upon the hash of the files.

https://arxiv.org/pdf/2208.05877.pdf
https://arxiv.org/pdf/2205.14927.pdf
https://arxiv.org/pdf/1407.3561.pdf
https://arxiv.org/pdf/2102.12737.pdf

>>>>

@@

@@

\subsection{BitTorrent}
\label{torrent}

BitTorrent originated in 2001.\footnote{We use torrent and BitTorrent interchangebly throughout this paper.} It was designed to make provision of common, large files more effecient. "When a file is made available using HTTP, all upload cost is placed on the hosting machine. With BitTorrent, when multiple people are downloading the same file at the same time, they upload pieces of the file to each other. This redistributes the cost of upload to downloaders, (where it is often not even metered), this making hosting a file with a potentially unlimited number of downloaders affordable."\cite{torrent} Publishers of files choose to make their file available as a torrent, where anyone with the proper software can download it.\footnote{Nowadays, even web browsers can use extensions to access torrents.\cite{webtorrent}} At launch, users would make .torrent files available - these files contained basic info about a file - the size, name, a tracker,\footnote{"Trackers are responsible for helping downloaders find each other. They speak a very simple protocol layered on top of HTTP in which a downloader sends information about what file it’s downloading, what port it’s listening on, and similar information, and the tracker responds with a list of contact information for peers which are downloading the same file."\cite{torrent}} and hashing info.\footnote{Since then, magnet links have become an option as well. These are specifically formatted links that provide the data needed to bootstrap a torrent download without pulling a file separate from the magnet link.}\cite{torrent} The original uploader must send out at least one copy of the file being shared (or it must already be distributed out of band), but after that, the file can be reconstructed from anyone sharing the torrent rather than the original provider. Users acquire peers in a random manner from trackers, ensuring robustness. Bittorrent divides files into small pieces of fixed size, which allows users to upload before a download is completed, and these pieces are known via their SHA1 hash, ensuring file integrity. Peers announce what files they have, resulting "in less than a tenth of a percent bandwidth overhead [while] reliably utiliz[ing] all available upload capacity.\cite{torrent} BitTorrent generally prioritizes the "rarest" pieces of a file first, based upon which peers have which pieces.\footnote{Though, users can customize the ordering if they choose to do so. Selecting the rarest first both ensures a full file is available, and it maximizes the sharing speed of a torrent, as once the rarest piece is acquired by a second peer, that peer can share that piece further.} BitTorrent reaches a relatively optimum end result through a mechanism known as choking: BitTorrent downloads from several peers - the fastest known peers - and optimistically probes for faster peers as well.\cite{torrent} BitTorrent effectively uses "tit-for-tat" exchange mechanisms to allow for a relatively distributed system which generally reaches optimal or near-optimal outcomes.

[TODO: mention more swap algorithms, see ipfs paper]

@@

[TODO: MainlineDHT]

\subsection{Crypto currencies}

@@

IPFS is a P2P system where files are shared based on the content of the files, rather than URLs (uniform resource locaters). URLs point to specific locations, which may host whatever those in charge of the location choose to serve, assuming you can route to the specific location to acquire a file.\footnote{Routing to blocked content is indeed the primary problem that we seek to solve in the censorship circumvention sphere.} Users of IPFS (either directly or an app that performs content acquisition under the hood using IPFS) request specific files, based upon the hash of the files. A key assumption of IPFS is that no nodes are priveleged or trusted specially, which leads to several design decisions based upon prior work. At it's core, IPFS provides basic utilities for identities, networking, routing, file exchange, object acquisition, file ststem management, and basic naming capabilities.\cite{ipfs}

A node in IPFS can be thought of as having an identity.\footnote{This identity can be refreshed as often as a user wants, though there is some benefit to using the same identity in the long run.} This identity is very basic: it's simply a lone node ID, which is the hash of a nodes public key. These keys are built using primitives from the S/Kademlia DHT.\footnote{S/Kademlia is an iteration of the Kademlia DHT. Kademlia DHT is designed to minimize the number of hops needed to learn the location of a desired address.\cite{kademlia} A large network of 10,000,000 nodes could be searched with 20 hops on average - queries are resolved in $\lceil log_2(n) \rceil$, where $n$ is the number of nodes in the network.\cite{ipfs} Additionally, Kademlia has low overhead for control messages, and had prior large usage.\cite{ipfs} S/Kademlia builds on Kademlia to reduce Sybil attacks by requiring some proof of work work (signatures) and allows for lookups in a more adversarial network - "S/Kademlia achieves a [lookup success] rate of .85 even with an adversarial fraction as large as half of the nodes."\cite{ipfs} S/Kademlia assumes an adversary similar to one which we do - an adversary can manipulate packets, do observation, etc. They can also generate an arbitrary number of adversarial nodes, and might attempt an eclipse attack.\cite{skademlia} The proof of work for generating a node-id is based upon putting some basic constraints on node-ids (e.g. certain bits must be 0), and therfore generating a valid node-id is doable for users, but is a configurable variable to stop an adversary.\cite{skademlia}} IPFS is designed to be transport agnostic - this is done using a \emph{multiaddr}, which is an identifier similar to a URL in terms of hierarchy, but providing networking information. For routing, IPFS must allow nodes to find other peers, and the location of specific content. IPFS draws on S/Kademlia and Coral DSHT's (distributed sloppy hash table) extensions to Kademlia for this - Coral DSHT notably reduces the overhead needed to find content by allowing for acquisition of just a single peer to acquire content, rather than needing to acquire every peer (hence, the \emph{sloppy} in the name). Coral also organizes content into clusters, which allows for more focused searching for content and reducing the latency of the network.

Content acquisition builds on BitTorrent. (See Section \ref{torrent} for more.) IPFS effectively uses the file sharing technology of torrenting, but instead of focusing on the pieces contained in a singular torrent, IPFS simply annonces all pieces it has, regardless of the original file. This means that files which share content may be acquired from multiple users, even if they don't have the exact same file as the user looking for the content (e.g. a user may be seeking a music album, but they may acquire a song from that album from a user who only has that song). A notable change from BitTorrent, BitSwap (the name of the content swapping protocol of IPFS) also encourages acquisition of generally rare files that users want, as by decoupling desired files from a torrent, users are incentivized to provide content that providers of the content they want are in search of, which results in a spread of rarer, more desired files in order to recieve better download speeds.\cite{ipfs}

IPFS builds a Merkle DAG on top of the DHT and content swapping technology. This DAG links via hashes of content - a generalization of the Git data structure.\cite{ipfs} Using this dag of hashes, IPFS has \emph{unique} identification of any objects, it is tamper resistent, and it allows for easy deduplication.\cite{ipfs} Content can be acquired using a very basic path format: /ipfs/<HASH>/<PATH TO OBJECT>. This format allows for easy integration into existing file systems, and for minor changes to allow for web browser usage (set up as: ipfs://<HASH>/<PATH TO OBJECT>). Users can add any object to the DHT, and may choose to \emph{pin} an object - marking it as an object that should be kept for the long run. Files are represented similar to Git files, with some minor additions added to improve performance. These changes include fast size lookups, deduplication of large files, and organizing commits into a tree.\cite{ipfs} A Git object can actually be converted to IPFS without losing any info, but not vice-versa.

So far, all of IPFS has been presented as immutable objects with a mutable networking structure, however, many applications require mutable objects to function properly, but IPFS would not support this, and would require extensive out-of-band communication in order to run anything using IPFS. A basic, mutable file addressing schema was introduces to provide every node-key to publish a single mutable file. This is done by allowing nodes to insert an arbitrary IPFS hash as /ipns/<Node ID>. The only mutable portion of IPFS is the routing system, which is used to publish this by adding the data as a singular, small metadata value.\cite{ipfs}

IPFS has been in use for several years, and has been used to run some services and provide some data on the web. [TODO: any censorship circumvention uses?] It has been implemented in both Golang and Javascript (with other languages in various states of completion), and is available in some prominent web browsers (Brave and Opera).\cite{ipfs-measure} The current version of IPFS uses a CID (content identifier) to point to objects - this is a variant of the hashes used to point to object. These CIDs include a multibase prefix - a prefix used to indicate the base the encoding used, a version identifier, a codec identifier (e.g. protobuf, JSON, etc), and a \emph{multihash} - a hah that indicates the hash algorithm used, and the length of the hash.\cite{ipfs-measure} IPFS uses a multiaddress to provide network addresses of peers - a flexible structure that allows conveying a full network address by first outlining the peer, their network protocol (and any data needed to use), the transport layer, and any additional transports that may reside on top of that.\cite{ipfs-measure} A couple sample multiaddresses are /ip4/<ip address>/tcp/<PORT>/ipfs/<Node ID> and /dns4/site.com/tcp/<PORT>/tls/ipfs/<Node ID>.

[TODO: Add stuff about current transports]

[TODO: Add section on uploading/retrieval]

[TODO: Mention gateways]

[TODO: SFS - self certified filesystems]

[TODO: Add chart from measurement paper]
